Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-09 tex/paper1/paper1.tex
edits to the paper

As noted in Section \ref{sec:anal}, the logarithm of the Fourier power for all
regions may be approximated by a normal distribution $N(\mu, \sigma)$.
The maximum likelihood estimate of the mean and variance of normal
distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
\label{eqn:sigmamean}
\end{equation}
where $N_{pixel}$ is the number of pixels in each region.

The estimated error in the estimated mean is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:errorsigmamean}
\end{equation}
where $N$ is the number of measurements taken.  This formula assumes
that the measurements taken are all independent of each other.
However, this is not the case for the Fourier power in any given
frequency.  This is because neighbouring pixels are highly likely to
be physically connected to each other, and so time-series in
neighboring pixels are likely to be strongly correlated (assuming that
the background structure exists over at least two pixels).  Secondly,
the point spread function of AIA spreads emission in one pixel over
its neighbors.  Therefore, the measurements used to generate an error
to the Fourier power are not independent.

Therefore, the number of effectively independent pixels is less than
the actual number of pixels used in any one region.  The number of
effective independent pixels is estimated in the following way.  The
cross correlation $c(\tau)$ function between two randomly chosen
next-nearest neighbor pixels is calculated.  The cross correlation
coefficient measures the linear dependence of two time series $X(t)$
and $Y(t \pm \tau)$ at different lags $\tau$.  This is used to define
a coefficient of independence between next nearest neighbor,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  The effect
number of independent pixels in region is given by
\begin{equation}
\label(eqn:nind}
N_{ind}= 1 + \rho(N_{pixel}-1)
\end{equation}
which is used in Equation \ref{eqn:errorsigmamean} to calculate the
estimated error in the mean.

>>>>

As noted in Section \ref{sec:anal}, the logarithm of the Fourier power
for all regions is approximated by a normal distribution $N(\mu,
\sigma)$.  The maximum likelihood estimate of the mean and variance of
normal distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
\label{eqn:sigmamean}
\end{equation}
where $N_{pixel}$ is the number of pixels in each region.  The
estimated error in the estimated mean is
\begin{equation}
\sqrt{\hat{\sigma_{d}^{2}}}/\sqrt{N}
\label{eqn:errorsigmamean}
\end{equation}
where $N$ is the number of measurements taken.  This formula assumes
that the measurements taken are all independent of each other.
However, this is not the case for the Fourier power in any given
frequency.  This is because neighbouring pixels are highly likely to
be physically connected to each other, and so time-series in
neighboring pixels are likely to be strongly correlated (assuming that
the background structure exists over at least two pixels).  Secondly,
the point spread function of AIA spreads emission in one pixel over
its neighbors.  Therefore, the measurements used to generate an error
to the Fourier power are not independent.

Therefore, the number of effectively independent pixels is less than
the actual number of pixels in any one region.  The number of
effective independent pixels is estimated in the following way.  The
cross correlation $c(\tau)$ function between two randomly chosen
next-nearest neighbor pixels is calculated.  The cross correlation
coefficient measures the linear dependence of two time series $X(t)$
and $Y(t \pm \tau)$ at different lags $\tau$.  This is used to define
a coefficient of independence between next nearest neighbor,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  The
effective number of independent pixels in region is given by
\begin{equation}
\label(eqn:nind}
N_{ind}= 1 + \rho(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{ind}$ in
Equation \ref{eqn:errorsigmamean}.  This gives a lengthscale for the
uncertainty in the mean Fourier \PS.

\subsection{Model fitting}

A three step fitting process is used to fit Models 1 and 2 to the
data.
\begin{enumerate}
\item Model 1 is fit to the data using the distribution widths
  $\sigma_{d}$.  Since this is much wider than the estimated error in
  the mean, it allows the fitting algorithm to converge to an
  approximate fit solution.
\item The estimated values to the model parameters are then used as
  initial guesses to the second fit of Model 1, assuming the much
  narrower estimated error $\sigma_{d}/\sqrt{N){ind}$.  This generates
  a better estimate to the parameters of the model fit.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma_{d}$, seeded with the maximum likelihood parameter values
  from Step 2 and the estimated $G(\nu)$ model parameters from Step 3.
\item Model 2 is fit to the data using the maximum likelihood model
  parameter values at Step 4 and the adjusted widths
  $\sigma_{d}/\sqrt{N){ind}$.
\end{enumarate}
